---
title: "EDA_Diamonds"
output: html_document
---

```{r}
getwd()

#Set Directory
setwd("/Users/Souvik Banerjee/Desktop/Data_Science/Data_Analyst_Nanodegree/3_EDA/3_EDA_Diamond")
```
## Load the data
```{r}
library(ggplot2)
data("diamonds")
summary(diamonds)
?diamonds

# To check the details of columns in dataset
str(diamonds)
```
## Histogram of the price of all the diamonds in the diamond data set.
```{r}
qplot(x = price, data = diamonds,
      color=('black'), fill=I('#FF9999'))
```
## Summary statistics of the price
```{r}
summary(diamonds$price)
```
## Diamonds Counts
```{r}
summary(diamonds$price < 500)
summary(diamonds$price < 250)
```
## largest peak in the price histogram
```{r}
qplot(x = price, data = diamonds, binwidth = 1000,
      color=('black'), fill=I('#FF9999')) +
  scale_x_continuous(limits = c(0,20000), breaks = seq(0,20000, 1000))
```
## save the plot
```{r}
ggsave('priceHistogram.png')
```
## histogram of diamond prices by cut
```{r}
qplot(x = price, data = diamonds, binwidth = 1000,
      color=('black'), fill=I('#FF9999')) +
  scale_x_continuous(limits = c(0,30000), breaks = seq(0,30000, 1000)) +
  facet_wrap(~cut)
```
## distribution for diamonds by cut
```{r}
# To change the y-axis
qplot(x = price, data = diamonds) + facet_wrap(~cut, scales = "free")
```
## histogram of price per carat and facet it by cut
```{r}
qplot( x = (diamonds$price/diamonds$carat), data = diamonds,
       color=('black'), fill=I('#FF9999'))+
  facet_wrap(~cut, scales = "free") +
  scale_x_log10()
```
## cut, price of diamonds using box plots
```{r}
qplot(x = cut, y = price, data = diamonds,
       geom = 'boxplot') +
  coord_cartesian(ylim = c(0,10000))
```
## color, price of diamonds using box plots
```{r}
qplot(x = color, y = price, data = diamonds,
      geom = 'boxplot') +
  coord_cartesian(ylim = c(0,10000))
```

## IQR
```{r}
IQR(subset(diamonds, price <1000)$price)
```













































































































