---
title: "2_Explore_one_variable"
output: html_document
---

``` {r}
getwd()
#change directory
setwd("/Users/Souvik Banerjee/Desktop/Data_Science/Data_Analyst_Nanodegree/3_EDA/2_Explore_one_variable")

#To see files
list.files()

# Read data
pf<- read.csv('pseudo_facebook.tsv', sep="\t")

names(pf)
```
## Create Histogram of Users Birthdays
``` {r}
# Import ggplot2
library(ggplot2)

#plot histogram
qplot(x=dob_day, data=pf) +
  scale_x_continuous(breaks = 1:31)

```
## Faceting
``` {r}
qplot(x = dob_day, data = pf) +
  scale_x_continuous(breaks = 1:31) +
  facet_wrap(~dob_month, ncol=4)

```
## Friend Count
``` {r}
qplot(x = friend_count, data = pf, xlim = c(0,1000))

# Different way to do the same plot
qplot( x = friend_count, data = pf) +
  scale_x_continuous(limits = c(0,1000))
```
## Adjusting the bin width
``` {r}
qplot(x = friend_count, data=pf, binwidth = 25) +
  scale_x_continuous(limits = c(0,1000), breaks = seq(0,1000, 50)) +
  facet_wrap(~gender)
```
## ommiting NA gender data
``` {r}
qplot(x = friend_count, data = subset(pf, !is.na(gender)), binwidth=25) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0,1000,50)) +
  facet_wrap(~gender)
```
## Statistics by gender
``` {r}
table(pf$gender)
by(pf$friend_count, pf$gender, summary)
```
## Tenure by months
``` {r}
qplot(x = tenure, data = pf, binwidth = 30,
      color = I('black'), fill=I('#099DD9'))
```
## Tenure by year
``` {r}
qplot(x = tenure/365, data = pf, binwidth = 0.25,
      color = I('black'), fill=I('#099DD9')) +
  scale_x_continuous(breaks=seq(1,7,1), limits=c(0,7))
```
## Labelling Plots
``` {r}
qplot( x = tenure/365, data = pf,  binwidth = 0.25,
       xlab = 'Number of years using Facebook',
       ylab = 'Number of users in sample',
       color = I('black'), fill=I('#099DD9')) +
  scale_x_continuous(breaks=seq(1,7,1), lim = c(0,7))
```
## Ages
``` {r}
qplot(x = age, data = pf, binwidth = 1,
      xlab = 'Age',
      ylab = 'Number of users in sample',
      color = I('black'), fill=I('#099DD9')) +
      scale_x_continuous(breaks = seq(13,113,5))
```
## 1 Column with 3 histogram
```{r}
# Grid library
library(gridExtra)
# first plot
p1 = qplot(x = friend_count, data = pf, binwidth = 25,
      xlab = 'Number of Friends',
      ylab = 'Number of users in sample',
      color = I('black'), fill=I('#099DD9')) +
  scale_x_continuous(limits = c(0, 1000), breaks = seq(0,1000,50))
#second plot
p2 = qplot(x = log10(friend_count), data = pf,
      color = I('black'), fill=I('#099DD9'))
# third plot
p3 = qplot(x = sqrt(friend_count), data = pf,
           color = I('black'), fill=I('#099DD9'))

grid.arrange(p1, p2, p3, ncol=2)
```
## 3 plots using ggplot
```{r}
# Import gridExtra
library(gridExtra)
q1 <- ggplot(aes(x = friend_count), data=pf) + geom_histogram()
q2 <- p1 + scale_x_log10()
q3 <- p1 + scale_x_sqrt()

grid.arrange(q1, q2, q3, ncol=2)
```
## Add a Scaling layer
```{r}
logScale <- qplot(x = log10(friend_count), data = pf)

countScale <- ggplot(aes(x = friend_count), data = pf) + 
  geom_histogram() +
  scale_x_log10()
  
p3 <- qplot(x = friend_count, data = pf) +
  scale_x_log10()

grid.arrange(logScale, countScale, p3, ncol = 2)
```
## Frequency ploygon
```{r}
qplot(x = friend_count, data = subset(pf, !is.na(gender)),
      binwidth = 10, geom = 'freqpoly', color = gender) +
  scale_x_continuous(breaks = seq(0, 1000, 50), lim = c(0,1000))
```
## Frequency polygon with proportions
```{r}
qplot(x = friend_count, y = ..count../sum(..count..), 
      data = subset(pf, !is.na(gender)),
      binwidth = 10, geom = 'freqpoly', color = gender,
      xlab = 'Friend Count',
      ylab = 'Proportions of Users with friend count') +
  scale_x_continuous(breaks = seq(0, 1000, 50), lim = c(0,1000))
```
## Frequency polygon to determine which gender makes more likes
```{r}
qplot(x = www_likes, data = subset(pf, !is.na(gender)), 
      geom = 'freqpoly', color = gender,
      xlab = 'Likes Count',
      ylab = 'Proportion of users with that friend count' ) +
  scale_x_log10()

```
## No. of likes 
```{r}
by(pf$www_likes, pf$gender, sum)
```
## Box plot
```{r}
qplot(x = gender, y = friend_count, data = subset(pf, !is.na(gender)), geom = 'boxplot') +
  coord_cartesian(ylim = c(0,1000))
```
# Numerical summary of the data
```{r}
by(pf$friend_count, pf$gender, summary)
```
## Friend request
```{r}
qplot(x = gender, y = friendships_initiated, data = subset(pf, !is.na(gender)), geom = 'boxplot')+
  coord_cartesian(ylim = c(0,200))
```
## Getting Logical
```{r}
summary(pf$mobile_likes)

summary(pf$mobile_likes > 0)

# create a new variable in the data frame with NA values.
mobile_check_in <- NA

pf$mobile_check_in <- ifelse(pf$mobile_likes > 0, 1,0)
pf$mobile_check_in <- factor(pf$mobile_check_in)
summary(pf$mobile_check_in)

# Total number of users mobile_check_in
length(pf$mobile_check_in)

# To find % who use mobile_check_in
sum(pf$mobile_check_in == 1) / length(pf$mobile_check_in)
```



